%% constraints.tex — operational constraints for many-to-many DRT with bidirectional meeting points
%% Many-to-Many DRT Bidirectional Meeting Point Paper
%% Symbols follow notation.tex exactly; no new symbols introduced.

\section*{Operational Constraints}

The following constraints define the feasibility region for the many-to-many DRT problem with
bidirectional meeting points. All constraints apply to accepted requests ($z_r = 1$) unless
otherwise noted. Constraint labels are used directly in the Phase~2 MILP formulation and the
fast feasibility checker.

% ---------------------------------------------------------------
\subsection*{Vehicle Capacity}

At no point in any vehicle's route may the number of passengers on board exceed the vehicle's
capacity.

\begin{equation}\label{con:capacity}
  q_v(i) \leq Q_v \quad \forall v \in \mathcal{V},\; \forall i \in \sigma_v
\end{equation}

where $q_v(i)$ is the passenger load on vehicle $v$ when departing from node $i$, and $Q_v$
is the vehicle's maximum capacity.

% ---------------------------------------------------------------
\subsection*{Time Windows}

Each accepted request must be picked up within its specified time window at the assigned pickup
meeting point.

\begin{equation}\label{con:tw-early}
  s_{v_r,\, m_r^P} \geq e_r \quad \forall r \in \mathcal{R},\; z_r = 1
\end{equation}

\begin{equation}\label{con:tw-late}
  s_{v_r,\, m_r^P} \leq l_r \quad \forall r \in \mathcal{R},\; z_r = 1
\end{equation}

where $s_{v_r,\, m_r^P}$ is the scheduled service time at pickup meeting point $m_r^P$ of
vehicle $v_r$, and $[e_r, l_r]$ is the pickup time window for request $r$.

% ---------------------------------------------------------------
\subsection*{In-Vehicle Ride Time}

The time a passenger spends riding in the vehicle (from pickup meeting point to dropoff meeting
point) must not exceed the maximum allowable ride time.

\begin{equation}\label{con:ridetime}
  s_{v_r,\, m_r^D} - s_{v_r,\, m_r^P} \leq L^{\max} \quad \forall r \in \mathcal{R},\; z_r = 1
\end{equation}

where $s_{v_r,\, m_r^D}$ is the scheduled service time at dropoff meeting point $m_r^D$, and
$L^{\max}$ is the maximum allowable in-vehicle ride time.

% ---------------------------------------------------------------
\subsection*{Walking Radius}

The assigned pickup and dropoff meeting points must lie within the maximum walking radius of
the passenger's origin and destination, respectively.

\begin{equation}\label{con:walk-pickup}
  d(o_r,\, m_r^P) \leq \rho^P \quad \forall r \in \mathcal{R},\; z_r = 1
\end{equation}

\begin{equation}\label{con:walk-dropoff}
  d(\delta_r,\, m_r^D) \leq \rho^D \quad \forall r \in \mathcal{R},\; z_r = 1
\end{equation}

where $d(o_r, m_r^P)$ is the Euclidean distance from origin $o_r$ to pickup meeting point
$m_r^P$, $\rho^P$ is the maximum pickup walking radius, and $\rho^D$ is the maximum dropoff
walking radius.

\textit{Note:} These constraints are equivalent to the candidate set filters $M_r^P$ and
$M_r^D$ defined in the problem setup; they are stated here explicitly to make the MILP
formulation complete.

% ---------------------------------------------------------------
\subsection*{Precedence: Pickup Before Dropoff}

For each accepted request, the pickup meeting point node must appear before the dropoff meeting
point node in the assigned vehicle's route, and the vehicle must serve the pickup before the
dropoff in time.

\begin{equation}\label{con:precedence-pos}
  \pi_r^P < \pi_r^D \quad \forall r \in \mathcal{R},\; z_r = 1
\end{equation}

\begin{equation}\label{con:precedence-time}
  s_{v_r,\, m_r^P} + t(m_r^P,\, m_r^D) \leq s_{v_r,\, m_r^D} \quad \forall r \in \mathcal{R},\; z_r = 1
\end{equation}

where $\pi_r^P$ and $\pi_r^D$ are the route insertion positions of the pickup and dropoff nodes
(both on vehicle $v_r$), and $t(m_r^P, m_r^D)$ is the travel time from pickup to dropoff
meeting point (a lower bound on the in-vehicle segment).

% ---------------------------------------------------------------
\subsection*{Route Time Consistency}

Scheduled service times must be consistent with travel times along each vehicle's route — the
vehicle cannot arrive at a node before it has had time to travel from the previous node.

\begin{equation}\label{con:time-consistency}
  s_{v,\, i+1} \geq s_{v,\, i} + t(\sigma_v(i),\, \sigma_v(i+1))
  \quad \forall v \in \mathcal{V},\; \forall i < |\sigma_v|
\end{equation}

where $\sigma_v(i)$ is the $i$-th node in vehicle $v$'s route, and
$t(\sigma_v(i), \sigma_v(i+1))$ is the travel time from the $i$-th to the $(i+1)$-th node.

% ---------------------------------------------------------------
\subsection*{Maximum Route Duration}

The total operating time of each vehicle from its first service node to its last must not
exceed the vehicle's maximum shift duration.

\begin{equation}\label{con:route-duration}
  s_{v,\, |\sigma_v|} - s_{v,\, 1} \leq T_v^{\max} \quad \forall v \in \mathcal{V}
\end{equation}

where $s_{v, 1}$ is the scheduled time at the first node in vehicle $v$'s route,
$s_{v, |\sigma_v|}$ is the scheduled time at the last node, and $T_v^{\max}$ is the maximum
allowable route duration (shift length) for vehicle $v$.

% ---------------------------------------------------------------
\subsection*{Domain Constraints}

The decision variables are restricted to the following domains.

\begin{align}
  z_r &\in \{0,1\} \quad &&\forall r \in \mathcal{R} \label{con:binary-z}\\
  v_r &\in \mathcal{V} \quad &&\forall r \in \mathcal{R},\; z_r = 1 \label{con:domain-v}\\
  m_r^P &\in M_r^P \quad &&\forall r \in \mathcal{R},\; z_r = 1 \label{con:domain-mp}\\
  m_r^D &\in M_r^D \quad &&\forall r \in \mathcal{R},\; z_r = 1 \label{con:domain-md}
\end{align}

% ---------------------------------------------------------------
\subsection*{Constraint Summary}

\begin{tabular}{lll}
\toprule
\textbf{Label} & \textbf{Class} & \textbf{Variables Involved} \\
\midrule
\ref{con:capacity}         & Vehicle Capacity            & $q_v(i)$, $Q_v$, $\sigma_v$ \\
\ref{con:tw-early}         & Time Windows (early)        & $s_{v_r, m_r^P}$, $e_r$ \\
\ref{con:tw-late}          & Time Windows (late)         & $s_{v_r, m_r^P}$, $l_r$ \\
\ref{con:ridetime}         & In-Vehicle Ride Time        & $s_{v_r, m_r^D}$, $s_{v_r, m_r^P}$, $L^{\max}$ \\
\ref{con:walk-pickup}      & Walking Radius (pickup)     & $d(o_r, m_r^P)$, $\rho^P$ \\
\ref{con:walk-dropoff}     & Walking Radius (dropoff)    & $d(\delta_r, m_r^D)$, $\rho^D$ \\
\ref{con:precedence-pos}   & Precedence (position)       & $\pi_r^P$, $\pi_r^D$ \\
\ref{con:precedence-time}  & Precedence (time)           & $s_{v_r, m_r^P}$, $s_{v_r, m_r^D}$, $t(m_r^P, m_r^D)$ \\
\ref{con:time-consistency} & Route Time Consistency      & $s_{v,i}$, $s_{v,i+1}$, $t(\sigma_v(i), \sigma_v(i+1))$ \\
\ref{con:route-duration}   & Maximum Route Duration      & $s_{v,1}$, $s_{v,|\sigma_v|}$, $T_v^{\max}$ \\
\ref{con:binary-z}         & Domain (acceptance)         & $z_r$ \\
\ref{con:domain-v}         & Domain (vehicle)            & $v_r$ \\
\ref{con:domain-mp}        & Domain (pickup point)       & $m_r^P$, $M_r^P$ \\
\ref{con:domain-md}        & Domain (dropoff point)      & $m_r^D$, $M_r^D$ \\
\bottomrule
\end{tabular}
