\begin{abstract}
Many-to-many demand-responsive transit (DRT) systems must balance route consolidation,
passenger convenience, and fleet responsiveness under uncertain request arrivals.
Meeting-point service designs can reduce routing intensity by consolidating passenger
pickups and dropoffs, but they also expose operators to acceptance losses when walking,
waiting, or in-vehicle burdens make an offer unattractive. This paper studies
bidirectional meeting-point DRT service design in which both pickup and dropoff
locations are selected from candidate meeting-point sets, passenger response is
represented through single-offer binary-logit acceptance, and vehicle routes are updated
through rolling-horizon operations.

We develop a passenger-response-aware simulation framework that links service offer
generation, binary-logit passenger response, and rolling-horizon dispatch. The framework
is used to compare door-to-door service, single-sided meeting-point service,
bidirectional service without choice, and the full passenger-response-aware design under
tested synthetic service-design conditions. The formal evidence is interpreted as
conditional operational evidence: bidirectional pickup and dropoff consolidation can
lower vehicle-kilometres per served trip when accepted requests are spatially compatible,
while also reducing served share and shifting rejection between passenger-choice and
routing-feasibility channels. Diagnostic coverage controls, fixed-accepted-set routing
decompositions, robustness checks, passenger-type heterogeneity analyses, post-hoc
welfare accounting, and algorithm diagnostics are treated separately from the primary
behavioral comparison.

The results support a logistics and operations reading of meeting-point DRT as a
service-design trade-off rather than an unconditional improvement. Under the tested
conditions, passenger-response-aware bidirectional meeting-point consolidation can
reduce routing intensity per served trip, but operators must monitor coverage loss,
choice rejection, feasibility rejection, and simulated passenger-type heterogeneity.
The study therefore contributes operational service-design evidence for many-to-many DRT
systems and clarifies the evidence boundaries for future empirical calibration and
public-data validation.
\end{abstract}

\begin{keywords}
demand-responsive transit \sep meeting points \sep passenger choice \sep rolling horizon \sep service design \sep logistics
\end{keywords}
