\section{Introduction}
\label{sec:intro}

Demand-responsive transit (DRT) provides flexible passenger service in areas where
fixed-route operations are difficult to sustain, but many-to-many door-to-door service
can create long vehicle tours, low vehicle utilization, and fragile schedules under
dynamic demand. Meeting-point service designs address this operational problem by asking
passengers to walk to designated pickup or dropoff locations so that vehicles can
consolidate routes. The same design choice also creates a passenger-response problem:
offers that reduce vehicle travel may be rejected when walking, waiting, in-vehicle
time, or fare burdens are too high. For logistics and operations management, the key
question is therefore not whether meeting points are always preferable, but how
bidirectional pickup and dropoff consolidation changes routing intensity, served share,
and rejection patterns under tested service-design conditions.

This paper studies a many-to-many DRT setting with bidirectional meeting-point sets.
For each request $r$, the operator constructs candidate pickup meeting points
$M_r^P$ near the origin and candidate dropoff meeting points $M_r^D$ near the
destination. The system then evaluates feasible service bundles, selects a routing-feasible
offer, presents a single offer to the passenger, and samples acceptance through a
binary-logit response model. Accepted requests enter a rolling-horizon dispatch process
that periodically reoptimizes active vehicle routes. This passenger-response-aware
simulation framework treats passenger response as an evaluation mechanism for generated
offers, not as an empirically calibrated behavioral validation or an endogenous routing
control.

The study is motivated by a gap between meeting-point DARP research and online DRT
operations. Prior meeting-point formulations have demonstrated the operational value of
walking flexibility, but they often focus on pickup-side consolidation or assume that
assigned meeting points are accepted. Dynamic DRT and rolling-horizon routing studies,
meanwhile, represent online fleet operations but generally retain door-to-door service or
deterministic request acceptance. Combining bidirectional meeting points, single-offer
binary-logit response, and rolling-horizon routing allows the paper to examine both sides
of the service-design trade-off: route consolidation among served trips and demand loss
through choice rejection or feasibility rejection.

The first contribution is a service-design formulation for many-to-many DRT with
bidirectional pickup and dropoff meeting points. The formulation separates candidate
meeting-point generation, feasible offer construction, passenger response, and dynamic
dispatch so that each design layer can be inspected against operational metrics. This
structure supports denominator-aware comparisons such as vehicle-km per served trip,
vehicle-km per original request, served share, choice rejection, and feasibility
rejection.

The second contribution is a passenger-response-aware simulation mechanism for
evaluating bidirectional meeting-point offers. The binary-logit layer represents
heterogeneous simulated passenger types and an outside option under a single-offer
mechanism. It does not claim empirical population calibration; instead, it makes explicit
how walking, waiting, in-vehicle time, and fare enter the acceptance evaluation and how
accepted requests become the realized input to rolling-horizon operations.

The third contribution is an evidence-bounded operational trade-offs narrative for
meeting-point DRT. Formal Phase 6 evidence is used to assess whether bidirectional
meeting-point consolidation can reduce routing intensity among served trips under tested
synthetic service-design conditions, while tracking coverage loss, passenger-response
trade-offs, and rejection decomposition. Matched-coverage controls,
fixed-accepted-set decompositions, robustness packages, passenger-type heterogeneity,
post-hoc welfare accounting, and algorithm diagnostics are treated as diagnostic or
supporting evidence rather than headline claims.

The remainder of this paper is organized as follows. Section~\ref{sec:literature}
positions the study within DARP, meeting-point DRT, passenger choice, and dynamic DRT
operations. Section~\ref{sec:model} defines the service-design model and binary-logit
response mechanism. Section~\ref{sec:algorithm} describes the rolling-horizon heuristic
and the simplified ex-post routing diagnostic. Section~\ref{sec:experiments} reports the
evidence layers and denominator-aware experimental narrative. Section~\ref{sec:policy}
discusses managerial and operational implications, and Section~\ref{sec:conclusion}
summarizes conditional findings, limitations, and future work.
