\begin{abstract}
Demand-responsive transit (DRT) offers flexible mobility in low-density urban areas,
but door-to-door service is operationally costly and difficult to scale.
Meeting-point-based DRT reduces vehicle detours by consolidating pickups and dropoffs
at pre-defined locations, yet existing work assigns meeting points only on the pickup
side and ignores passenger heterogeneity in mode choice.
We address this gap by proposing a many-to-many DRT model with bidirectional meeting
point sets ($M_r^P$ for pickup, $M_r^D$ for dropoff) and explicit binary logit
passenger choice with three passenger types and an outside option.
The model is formulated as a coupled three-layer system — service offer generation,
passenger response, and dynamic dispatch — and solved with a Mixed-Integer Linear
Program (MILP) exact benchmark for small instances and a rolling horizon Adaptive
Large Neighbourhood Search (ALNS) heuristic for large-scale deployment.
Numerical experiments on synthetic scenarios calibrated to Chinese suburban conditions
show that, at equal served share ($\approx$22.8\%), the full bidirectional model
achieves \textbf{11.1\,vkm/trip} compared to \textbf{17.1\,vkm/trip} for the
DoorToDoor\,(capped) baseline --- a \textbf{35.0\%} improvement in per-trip vehicle
utilisation that cannot be attributed to coverage differences (endogenous
matched-coverage comparison). Under the unconstrained comparison (FullModel 20.8\%
vs.\ DoorToDoor 61.0\% served share), FullModel achieves 15.1\,vkm/trip versus
21.3\,vkm/trip (29.2\% improvement). For reference, a post-hoc matched-coverage
estimate yields 10.9 vs.\ 42.3\,vkm/trip (74.3\% improvement), providing a
conservative lower bound.
Equity analysis across passenger types reveals a Gini coefficient of 0.1216 in
acceptance rates: time-sensitive passengers are systematically disadvantaged
(14.4\% acceptance) relative to price-sensitive (25.4\%) and walk-sensitive (20.2\%)
passengers.
Based on these findings, we derive five actionable policy recommendations for Chinese
city DRT operators, including a walking radius threshold of 1000~m for viable
bidirectional deployment and a minimum fleet ratio of 15 vehicles per 100 daily
requests.
\end{abstract}

\begin{keyword}
demand-responsive transit \sep meeting points \sep passenger choice \sep ALNS \sep rolling horizon \sep equity
\end{keyword}
